\input{preamble}

\mytitle{Curriculum Vitae}
\definecolor{color1}{rgb}{0.0, 0.45, 0.81}
\definecolor{mark_color}{rgb}{0, 0, 0}

\begin{document}
\pagestyle{headonly}

\makecvtitle

\cvitem{}{\emph{\vspace{-1cm}\\
$\quad$ Relativistic astrophysicist, studying the impact of Einstein's general relativity on the astrophysical world. Research interests include gravitational-wave astronomy, black-hole binary dynamics, Bayesian statistics, and machine-learning applications.}}

\section{Contact}

\cvitem{Email}{\href{mailto:davide.gerosa@unimib.it}{davide.gerosa@unimib.it}}
\cvitem{Address}{Universit\`{a} degli Studi di Milano-Bicocca, Piazza della Scienza 3, 20126 Milano, Italy.}
\cvitem{Website}{\href{https://www.davidegerosa.com/}{www.davidegerosa.com}}

%\cvitem{Citizenship}{Italy, EU.}

%\section{Current academic positions}
\section{Academic positions}

\cventry{2021 - current}{Associate Professor (Professore Associato), Department of Physics}{Universit\`{a} degli Studi di Milano-Bicocca}{Milan, Italy}{}{}
\vspace{-0.1cm}
\begin{tabular}{rcl}
&\hspace{0.4cm} &$\circ\;\;${\textit{Responsibilities}}: Group leader of ERC project ``\textit{GWmining}''; undergraduate and graduate teaching; \\&\hspace{0.4cm} &
\hspace{0.4cm}
PhD, MSc and BSc thesis advisor; postdoc line manager.
\end{tabular}
\vspace{0.2cm}

%\section{Past academic positions}


\cventry{2019-2021}{Assistant Professor (Lecturer), Institute for Gravitational Wave Astronomy}{University of Birmingham}{Birmingham, UK}{}{}
\vspace{-0.1cm}
\begin{tabular}{rcl}
&\hspace{0.4cm} &$\circ\;\;${\textit{Responsibilities}}: Research-focused appointment; graduate and undergraduate teaching; \\&\hspace{0.4cm} &  
\hspace{0.4cm}
MSc and PhD student mentoring; postdoc line manager; BSc student tutoring.\\
\end{tabular}


\vspace{0.2cm}

\cventry{2016-2019}{Postdoctoral scholar, NASA Einstein Fellow}{California Institute of Technology}{Pasadena CA, USA}{}{}
\vspace{-0.1cm}
\begin{tabular}{rcl}
&\hspace{0.4cm} &$\circ\;\;${\textit{Support}}: Einstein postdoctoral prize fellowship.  Part of the NASA prize fellowship program, Einstein\\
&\hspace{0.4cm} &  \hspace{0.4cm}Fellowships are prestigious awards in theoretical astrophysics consisting of personal research grant at\\
&\hspace{0.4cm} &  \hspace{0.4cm}selected US institution. See  \href{http://cxc.cfa.harvard.edu/fellows}{\texttt{cxc.cfa.harvard.edu/fellows}}.\\
\end{tabular}


\section{Education}

\cventry{2013-2016}{Ph.D., Department of Applied Mathematics and Theoretical Physics}{University of Cambridge}{Cambridge, UK}{}{}
\vspace{-0.1cm}
\begin{tabular}{rcl}
&\hspace{0.4cm} &$\circ\;\;${\textit{Support}}: Isaac Newton Studentship; STFC Ph.D. Studentship. The
Isaac Newton Studentship is the \\&\hspace{0.4cm} &  
\hspace{0.4cm}only astronomy-specific Ph.D. scholarship of the University of Cambridge.\\
&\hspace{0.4cm} &$\circ\;\;${\textit{Supervisor}}: U. Sperhake. Thesis resulted in 14 publications.
\suppress \cite{2016PhDT.......177G} \endsuppress %ADSkey
%\suppress \cite{Gerosa:2016joa} \endsuppress %INSPIREkey
\\
\end{tabular}

\vspace{0.2cm}
\cventry{2010-2013}{Master's degree in Astrophysics}{\newline Universit\`{a} degli Studi di Milano}{Milan, Italy}{}{}
\vspace{-0.1cm}
\begin{tabular}{rcl}
&\hspace{0.4cm} &$\circ\;\;${\textit{Final degree grade}}: 110/110 with distinction (``cum laude'').\\
&\hspace{0.4cm} &$\circ\;\;${\textit{Average class grade}}: 30.00/30 with 7/12 distinctions (``cum laude'').\\
&\hspace{0.4cm} &$\circ\;\;${\textit{Thesis advisors}}: E. Berti, G. Lodato. Thesis resulted in 2 publications.\\

\end{tabular}

\vspace{0.2cm}
\cventry{2007-2010}{Bachelor's degree in Physics}{Universit\`{a} degli Studi di Milano}{Milan, Italy}{}{}
\vspace{-0.1cm}
\begin{tabular}{rcl}
&\hspace{0.4cm} &$\circ\;\;${\textit{Final degree grade}}: 110/110 with distinction (``cum laude'').\\
&\hspace{0.4cm} &$\circ\;\;${\textit{Average class grade}}: 29.84/30 with 18/26 distinctions (``cum laude'').\\
%&\hspace{0.4cm} &$\circ\;\;${\textit{Thesis advisor}}:  D. Klemm.\\
\end{tabular}


\vspace{0.2cm}
\cventry{2002-2007}{Scientific High School degree}{\newline Liceo Scientifico Statale Paolo Frisi}{Monza, Italy}{}{}  %
\vspace{-0.1cm}
\begin{tabular}{rcl}
&\hspace{0.4cm} &$\circ\;\;${\textit{Final grade}}:  100/100.\\
\end{tabular}

\newpage{}
%\vspace{0.2cm}
\textbf{\textcolor{black}{Internships:}}\vspace{0.05cm}\\
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Institut Astrophysique de Paris, Paris, France.}{Jul 2015} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ University of Mississippi, Oxford MS, USA.}{Aug-Dec 2012} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Caltech, Pasadena CA, USA. LIGO Summer Undergraduate Research Fellow (SURF).}{Jun-Aug 2012}




\section{Metrics}

\input{metricspapers.tex}

\textbf{Full list of publications} available 
%mark_CVshort
below and
%mark_CVshort
at \href{http://www.davidegerosa.com/pub}{\texttt{www.davidegerosa.com/pub}}.

\vspace{0.2cm}

\input{metricstalks.tex}

\textbf{Full list of presentations} available
%mark_CVshort
below and
%mark_CVshort
at \href{http://www.davidegerosa.com/talks}{\texttt{www.davidegerosa.com/talks}}.

\section{Grants}
For collaborative grants, the reported amount refers to the portion awarded to my unit/group. 
\vspace{0.3cm}

\cvitemwithcomment{}{\textbf{Italian-French University (UIF/UFI) - Chapter 3 Grant}. Co-I unit leader, 78k EUR, No.~2025-C3-386.}{2025-2029}\vspace{-0.05cm}
\cvitemwithcomment{}{\hspace{0.6cm}\textit{``Populations of compact objects for next-generation gravitational-wave detectors''}}{}

\cvitemwithcomment{}{\textbf{European Research Council (ERC) -- Starting Grant}. PI, 1.5M EUR, No.~945155--GWmining.}{2021-2026}\vspace{-0.05cm}
\cvitemwithcomment{}{\hspace{0.6cm}\textit{``Gravitational-wave data mining''}}{}

\cvitemwithcomment{}{\textbf{Ministero Universit\`a e Ricerca (MUR) -- PRIN Grant}. Co-I unit leader, 85k EUR. No. 2022-Z9X4XS}{2023-2025}\vspace{-0.05cm}
\cvitemwithcomment{}{\hspace{0.6cm}\textit{``
Gravitational-wave astronomy as a mature field: selection biases and environmental effects''}}{}


\cvitemwithcomment{}{\textbf{Cariplo Foundation -- Excellence Attractiveness Grant}. PI, 330k EUR, No.~2021-0555.}{2021-2026}\vspace{-0.05cm}
\cvitemwithcomment{}{\hspace{0.6cm}\textit{``Deep into the relativistic two-body problem''}}{}



\cvitemwithcomment{}{\textbf{Leverhulme Trust -- Research Project Grant}. PI, 190k GBP, No.~RPG-2019-350.}{2020-2023}\vspace{-0.05cm}
\cvitemwithcomment{}{\hspace{0.6cm}\textit{``Black-hole spins and accretion discs with gravitational waves from space''}}{}

\cvitemwithcomment{}{\textbf{Royal Society -- Research Grant}. PI, 20k GBP, No.~RGS-R2-202004.}{2020-2021}\vspace{-0.05cm}
\cvitemwithcomment{}{\hspace{0.6cm}\textit{``The supermassive black-hole binary puzzle: putting the pieces together''}}{}




\section{Awards}

\textbf{\textcolor{black}{Career prizes:}}
\vspace{0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
Frontiers of Science Award (Physics), International Congress of Basic Science, Beijing, China.}{2025}
\vspace{-0.1cm}


\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
SIGRAV Prize for Young Researchers, Italian Society of General Relativity and Gravitational Physics.}{2021}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
Research Prize of the Italian Minister of Cultural Heritage, Lincei National Academy.}{2020}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{IUPAP GRG Young Scientist Prize}, International Society for General Relativity and Gravitation.}{2020}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{Giulio Rampa PhD Thesis Prize}, Italian Society of General Relativity and Gravitational Physics.}{2018}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{Stefano Braccini PhD Thesis Prize}, Gravitational Wave International Committee (GWIC).}{2017}
\vspace{-0.1cm}

\vspace{0.2cm}
\textbf{\textcolor{black}{Personal scholarships:}}
\vspace{0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{Einstein Postdoctoral Prize Fellowship}, NASA.}{2016-2019}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{Isaac Newton PhD Studentship}, DAMTP \& IoA, University of Cambridge.}{2013-2016}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{STFC PhD Studentship}, UK Science \& Technology Facilities Council.}{2013-2016}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{Rouse Ball Studentship in Mathematics}, Trinity College, University of Cambridge.}{2015}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{LIGO Summer Undergraduate Research Fellowship (SURF)}, California Institute of Technology.}{2012}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{Undergraduate Studentship}, Physics Department, University of Milan.}{2007-2008}
\vspace{-0.1cm}


\newpage
%%%%%%%
%\vspace{0.2cm}

\textbf{\textcolor{black}{Other funding:}}
\vspace{0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{Fondo Ateneo Quota Competitiva (internal competitive grant at Milano-Bicocca)}, 15k EUR.}{2025}%\vspace{-0.1cm}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{\textbf{Marie Skłodowska-Curie Fellowship}} (EU), supervisor for candidate Z. Roupas, 188k EUR.}{2024}%
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{\textbf{Marie Skłodowska-Curie Fellowship}} (EU), supervisor for candidate A. Renzini, 188k EUR.}{2023}%
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{Fondo Ateneo Quota Competitiva (internal competitive grant at Milano-Bicocca)}, 25k EUR.}{2023}%\vspace{-0.1cm}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{CINECA ISCRA Type-B project}, 1.2M CPUh at the Italian National HPC center.}{2022}%\vspace{-0.1cm}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{Stephen Hawking Fellowship (UK)}, supervisor for candidate S. Baghwat, 460k GBP.}{2022}%
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{HPC Baskerville pilot project}, early GPU access at UK Tier 2 cluster.}{2021}%\vspace{-0.1cm}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
{Undergraduate summer student support}, Royal Astronomical Society (UK), 1k GBP.}{2020}%\vspace{-0.1cm}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$
{HPC Midlands+ substantial project}, 3M CPUh at UK Tier 2 cluster.}{2020}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$
{NSF Grant PHY-1759835}, National Science Foundation (USA), 10k USD.}{2018}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$
{Travel Grant}, Royal Astronomical Society, UK.}{2016}
\vspace{-0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$
{Smith-Rayleigh-Knight Essay Prize}, Faculty of Mathematics, University of Cambridge.}{2015}

%\cventry{2014-2015}{Darwin College}{Travel fund}{Cambridge, UK}{University of Cambridge}{}
%\cventry{2015}{Cambridge Philosophical Society}{Travel fund}{Cambridge, UK}{University of Cambridge}{}
%\cvitem{Nov 2011}{Award assigned by the cultural association "Famiglia Legnanese" to  best Italian College students, Legnano MI, Italy.}
%\cvitem{Jul 2007}{Award assigned by the website \textit{matematicamente.it} to the best italian high-school research project, presenting my work  {"Do I Dare disturb the Universe?"} about  evidences for dark matter.}

\section{Research group} %\vspace{0.2cm} 

\input{parsegroup.tex}



\section{Teaching}

%\vspace{0.1cm}
\textbf{\textcolor{black}{Taught classes:}}
\vspace{0.1cm}
\\
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Machine learning applied to physical systems.}}{2024-current} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Artificial Intelligence BSc, Pavia+Milano+Milano-Bicocca joint degree.}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ 
\href{https://dgerosa.github.io/machinelearning4physics}{\texttt{dgerosa.github.io/machinelearning4physics}}}{} 
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Scientific computing with python}.
% (113R-06).
}{2023-current} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Physics PhD, Milano-Bicocca.}{} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$
\href{https://dgerosa.github.io/scientificcomputing}{\texttt{dgerosa.github.io/scientificcomputing}}}{} 
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Astrostatistics and machine learning}.% (F5802Q014/20).
}{2022-current} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Astrophysics and Space Science MSc, Milano-Bicocca.}{} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$
\href{https://dgerosa.github.io/astrostatistics}{\texttt{dgerosa.github.io/astrostatistics}}}{} 

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Classical physics.} %(E3101Q130).
}{2021-2023} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Computer Science BSc, Milano-Bicocca.}{} 

\newpage


\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Year 1 Astrolab}.}{2020-2021} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Physics BSc, Birmingham.}{} 


\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Year 1 student tutoring}.}{2019-2021} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Physics BSc, Birmingham.}{} 


\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Black holes and gravitational waves}.}{2019-2020} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Midlands Physics Alliance Graduate School (MPAGS) PhD, Birmingham.}{} 


\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Part III General relativity}  (teaching assistant).}{2015-2016} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Mathematics MSc, Cambridge.}{} 

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Part II General relativity}  (teaching assistant).}{2014-2016} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Natural Sciences BSc, Cambridge.}{} 


\vspace{0.2cm}
\textbf{\textcolor{black}{Teaching qualifications:}}\vspace{0.05cm}\\
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ UK Postgraduate Certificate in Higher Education (PGCHE). Graduated with distinction.}{2019-2021} 



\section{Service}




\textbf{\textcolor{black}{Journal referee}}\vspace{0.1cm}\\
\begin{tabular}{@{\hskip 0.4cm}l@{\hskip 0.4in}l}
$\circ\;$ Nature Astronomy,  & $\circ\;$   Reports on Progress in Physics,  \\
$\circ\;$ Nature Communications,  & $\circ\;$   European Physical Journal Plus,   \\
$\circ\;$ Science, & $\circ\;$ European Physical Journal C,  \\
$\circ\;$ Science Advances, & $\circ\;$  Europhysics Letters, \\
$\circ\;$ Physical Review Letters, & $\circ\;$  Physics Letters A, \\
$\circ\;$ Physical Review D,  & $\circ\;$   Scientific Reports, \\
$\circ\;$  The Astrophysical Journal Letters,  &  $\circ\;$ Annals of Physics \\
$\circ\;$ The Astrophysical Journal,  &  $\circ\;$ Astrophysics and Space Science, \\
$\circ\;$  Monthly Notices of the Royal Astronomical Society, & $\circ\;$ Journal of Open Source Software,  \\
$\circ\;$  Classical and Quantum Gravity, & $\circ\;$ SoftwareX, \\
$\circ\;$  Astronomy \& Astrophysics & $\circ\;$Taylor and Francis Press (textbooks).  \\
$\circ\;$  General Relativity and Gravitation, & %$\circ\;$  \\
\end{tabular}

\vspace{0.2cm}

I refereed papers written by the LIGO/Virgo/KAGRA Collaboration, the NanoGRAV Collaboration, and the SXS Collaboration.


\vspace{0.2cm}



% Also Universe, Galaxies, Symmetry

 \textbf{\textcolor{black}{Journal editor}}\vspace{0.1cm}\\
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Classical and Quantum Gravity, Focus Issue \textit{``Numerical Relativity Beyond General Relativity".}}{2019} \vspace{-0.1cm}
\vspace{0.2cm}


 \textbf{\textcolor{black}{Grant proposal reviewer}}. Panel memberships marked with *.\vspace{0.1cm}\\
 %
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ ERC, Starting Grants, European Union;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ ERC, Advanced Grants, European Union;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ COST Actions, European Union;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ ESA, Voyage 2050 Topical Teams, Europe;*}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ NASA, Astrophysics Theory Program (ATP), USA;*}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ NASA, Postdoctoral Program (NPP), USA;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ NASA, Graduate Fellowship Program (NESSF/FINESST), USA;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ NSF, CAREER program, USA;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ NSF, Physics Division, USA;*}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ NSF, Astronomy Division, USA;*}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ STFC, Gravitational Waves Consolidated Grant Panel, UK;*}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ STFC, Astronomy Consolidated Grant Panel, UK;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ STFC, Rutherford Fellowships, UK;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ EPSRC, Hawking Fellowships, UK;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Royal Society, University Research Fellowships, UK;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ STFC, DiRAC HPC cluster, UK;*}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ MUR, Montalcini Fellowships, Italy;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Cariplo Foundation, Italy;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Humboldt Research Fellowships, Germany;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Dim Origines Grants, France;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ NWO, Veni Fellowships, The Netherlands;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Swiss NSF, Ambizione Fellowships, Switzerland;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Irish Research Council, Laureate Programme, Ireland;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Fonds de la Recherche Scientifique, Grants and Fellowship Call, Belgium;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ National Science Centre, Poland;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Research Grants Council, Hong Kong.}{}
\vspace{-0.1cm}
 
%\begin{tabular}{@{\hskip 0.4cm}l}
%$\circ\;$ \\
%$\circ\;$ ERC, Advanced Grants, Europe;\\
%$\circ\;$ ESA, Voyage 2050 Topical Teams, Europe;* \\
%$\circ\;$ NASA, Astrophysics Theory Program (ATP), USA;* \\
%$\circ\;$ NASA, Postdoctoral Program (NPP), USA;\\
%$\circ\;$ NASA, Graduate Fellowship Program (NESSF/FINESST), USA; \\
%$\circ\;$ NSF, CAREER program, USA;\\
%$\circ\;$ NSF, Physics Division Grants, USA;\\
%$\circ\;$ STFC, Astronomy Grant Panel (AGP Consolidated), UK;\\
%$\circ\;$ STFC, Rutherford Fellowships, UK;\\
%$\circ\;$ Royal Society, University Research Fellowships, UK;\\
%$\circ\;$ STFC, DiRAC HPC cluster, UK;*\\
%$\circ\;$ Irish Research Council, Laureate Programme, Ireland;\\
%$\circ\;$ Fonds de la Recherche Scientifique, Grants and Fellowship Call, Belgium;\\
%$\circ\;$ Research Grants Council, Hong Kong.
%\end{tabular}


\vspace{0.2cm}
%\newpage{}
\textbf{\textcolor{black}{Hiring board member}} for University of Birmingham (UK), University of Milano-Bicocca (Italy), Sapienza University \\ \phantom{xx} of Rome (Italy), University of Padua (Italy). 
%\vspace{-0.1cm}

\vspace{0.2cm}
\textbf{\textcolor{black}{PhD thesis examiner}} for SISSA (International School for Advanced Studies; Italy), Imperial College London (UK),
 \\ \phantom{xx} Monash University (Australia),  Cardiff University (UK), 
 University of Pisa (Italy), University of Milan (Italy). %\vspace{-0.1cm}


\vspace{0.2cm}
\textbf{\textcolor{black}{Organized conferences}}\vspace{0.05cm}\\
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ XXVI SIGRAV conference on general relativity and gravitation}{2025}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ University of Milano-Bicocca, Italy. \href{https://sites.google.com/unimib.it/sigrav2025}{\texttt{[link]}}
}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Theoretical Horizons in Unraveling Relativity, Astrophysics, and Mergers (THURAM).
}{2024}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Gran Sasso Science Institute, Italy. \href{https://davidegerosa.com/thuram/}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Gravitational-wave snowballs, populations, and models}{2025}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Sexten Center for Astrophysics, Italy. \href{https://sites.google.com/unimib.it/gwsnowballs}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Challenges and future perspectives in gravitational-wave astronomy: O4 and beyond}{2024}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$  Lorentz Center, Leiden, the Netherlands. \href{https://www.lorentzcenter.nl/challenges-and-future-perspectives-in-gravitational-wave-astronomy-o4-and-beyond.html}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Linking Advances in our Understanding of Theoretical Astrophysics and Relativity to Observations}{2024}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$  (LAUTARO). University of Milano-Bicocca, Italy. \href{https://davidegerosa.com/lautaro/}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Big data within science and industry.}{2023}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ University of Milano-Bicocca, Italy. \href{https://sites.google.com/unimib.it/bigdatamasterclass}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Gravitational-wave populations: what's next?}{2023}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ University of Milano-Bicocca, Italy. \href{https://sites.google.com/unimib.it/gwpopnext}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Gravitational-wave Excellence Alliance Training (GrEAT) PhD school.}{2019}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ University of Birmingham, UK. \href{https://sites.google.com/view/greatnetworkschool}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Numerical Relativity beyond General Relativity.}{2018}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Benasque Science Center, Benasque, Spain. \href{https://www.benasque.org/2018relativity}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ APS 34$^\textsf{th}$ Pacific Coast Gravity Meeting.}{2018}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Caltech, USA. \href{http://www.tapir.caltech.edu/~pcgm34}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ The migration issue: from protoplanets to supermassive black holes.}{2017}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ University of Cambridge, UK. \href{https://www.kicc.cam.ac.uk/events/copy_of_past-events/the-migration-issue-from-protoplanets-to-supermassive-black-holes-1/the-migration-issue-from-protoplanets-to-supermassive-black-holes}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Einstein's Legacy: Celebrating 100 $\!$yrs of General Relativity.}{2015}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Queen Mary University of London, UK.}{} \vspace{-0.1cm}


%\newpage{}

%

%\textbf{\textcolor{black}{Outreach activities}}\vspace{0.05cm}\\
%\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ TV Interview on gravitational waves and black-hole kicks aired on Cambridge TV.}{2016}\vspace{-0.1cm}
%\cvitem{}{\hspace{0.8cm}(see \href{http://www.cambridge-tv.co.uk/davide-gerosa-black-holes/)}{\textit{cambridge-tv.co.uk/davide-gerosa-black-holes}}).\vspace{-0.1cm}}
%\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Actively involved in the Cambridge Science Festival, faculty of Mathematics.}{2015}\vspace{-0.1cm}
%\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Research coverage by the Caltech outreach journal: CURJ, Vol.15 No.1 (2014).}{2014}\vspace{-0.1cm}
%\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Scientific journalist for the Italian on-line newspaper \href{http://www.ilsussidiario.net}{\textit{ilsussidiario.net}.}}{since 2013}\vspace{-0.1cm}
%\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  Astronomy and relativity lectures to high-school students.}{since 2011}\vspace{-0.1cm}

%



%\newpage
\vspace{0.2cm}
\textbf{\textcolor{black}{Professional recognition and service}}\vspace{0.05cm}
\\
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Erasmus program coordinator, Physics department, University of Milano-Bicocca.}{2024 - current}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  European Consortium for Astroparticle Theory (EuCAPT), council member.}{2022 - current}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  Italian Habilitation  to Full Professorship in Astrophysics (ASN 02/C1).}{2022}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  Italian Habilitation  to Full Professorship in Theoretical Physics (ASN 02/A2).}{2022}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  Italian Habilitation  to Associate Professorship in Astrophysics (ASN 02/C1).}{2020}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  Italian Habilitation  to Associate Professorship in Theoretical Physics (ASN 02/A2).}{2018}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  Seminar organizer, AstroBicocca seminar series, Milano-Bicocca.}{2021-2024}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Academic advisory team for the BlueBEAR HPC cluster, Birmingham.}{2019-2021}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  Seminar organizer, TAPIR seminar series, Caltech.}{2018-2019}\vspace{-0.1cm}
%\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Caltech representative, committee of the European COST Action ``GWverse''.}{2017-2019}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  PhD student representative, Gravitational Physics committee, UK Institute of Physics.}{2014-2016}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  Undergraduate student representative, Physics Department, University of Milan.}{2008-2012}\vspace{-0.1cm}


%$\circ\;$ GWIC 3G Science case subcommittee, & $\circ\;$ Royal Astronomical Society,\\

%\vspace{0.2cm}
\newpage
\textbf{\textcolor{black}{Memberships}}\vspace{0.05cm}\\
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ International Society on General Relativity and Gravitation (ISGRG), life member.}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Italian Society of General Relativity and Gravitational Physics (SIGRAV), honorary life member.}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ International Astronomical Union (IAU), Individual member.}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ American Physical Society (APS), member.}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Italian Physical Society (SIF), member.}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ European Astronomical Society (EAS), member.}{}\vspace{-0.1cm}
%\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Association of ERC Grantees (AERG), member.}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Italian Center for Supercomputing (ICSC).}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ TEONGRAV National Initiative (Gravity Theory), Italian National Institute for Nuclear Physics (INFN).}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ AI\_INFN National Initiative (Artificial Intelligence), Italian National Institute for Nuclear Physics (INFN).}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ LISA Consortium, community member.}{}\vspace{-0.1cm}

\vspace{-0.32cm}

\section{Skills}
\cvitem{Programming languages}{Python (advanced), Bash, Mathematica, C. 
}
\cvitem{Other scientific tools}{TensorFlow, LIGO lalsuite, LaTex, git, slurm, cloud computing, website development.}
\cvitem{Languages}{English (fluent), Italian (native).}

\vspace{-0.32cm}
\section{Hobbies}
Alpinism, rock climbing, skiing. Climbed to the top of Monte Rosa, 2nd highest mountain in the Alps (next~dream: the Matterhorn). In love with the US National Parks. Bruce Springsteen fanatic.  Too many fantasy \& sci-fi books, Tex~Willer comics. Avid soccer player, FC Inter fan. Some running as well. Very poor attempts at~photography.

%mark_CVshort

\pagebreak
\section{Full publication list}\vspace{0.2cm} 

\input{parsepapers.tex}

\pagebreak
\section{Full presentation list}\vspace{0.2cm} 

\input{parsetalks.tex}
%mark_CVshort

\end{document}
