Invited talks marked with *.
\vspace{0.2cm}

\textcolor{color1}{\textbf{Talks at conferences:}}
\vspace{-0.5cm}

\cvitem{}{\small\hspace{-1cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
%
\textbf{60.} & * & \textit{You’ll never merge alone.}
\newline{}
Unsolved problems in astrophysics and cosmology, Jerusalem, Israel, Dec 2022.
\vspace{0.05cm}\\
%
\textbf{59.} &  & \textit{Characterization of LIGO/Virgo selection effects with neural networks.}
\newline{}
Machine learning in GW search: g2net next challenges, Pisa, Italy, Sep 2022.
\vspace{0.05cm}\\
%
\textbf{58.} &  & \textit{Machine learning and the origin of LIGO's black holes.}
\newline{}
31th Texas Symposium on Relativistic Astrophysics, Prague, Czechia, Sep 2022.
\vspace{0.05cm}\\
%
\textbf{57.} & * & \textit{Gravitational-wave populations with a pinch of deep learning.}
\newline{}
23nd International Conference on General Relativity and Gravitation (GR23), Beijing, China, (online), Jul 2022.
\vspace{0.05cm}\\
%
\textbf{56.} &  & \textit{Accretion disks around supermassive black-hole binaries can break.}
\newline{}
EuCAPT workshop: Gravitational-wave probes of black hole environments, Rome, Italy, Jun 2022.
\vspace{0.05cm}\\
%
\textbf{55.} & * & \textit{Black-hole binary spin precession: new theoretical predictions and current observational evidence.}
\newline{}
9th KAGRA international workshop, Beijing, China, (online), Jun 2022.
\vspace{0.05cm}\\
%
\textbf{54.} & * & \textit{A deep-learning solution to the gravitational-wave population problem.}
\newline{}
NBIA Workshop on black-hole dynamics: from gaseous environments to empty space, Copenhagen, Denmark, Jun 2022.
\vspace{0.05cm}\\
%
\textbf{53.} &  & \textit{Gravitational-wave populations and black-hole spin time travel.}
\newline{}
April APS Meeting, New York NY, USA Apr 2022, Apr 2022.
\vspace{0.05cm}\\
%
\textbf{52.} & * & \textit{I've seen a deviation from General Relativity: do you believe me?.}
\newline{}
4th Milan Christmas Workshop, Milan, Italy, Dec 2021.
\vspace{0.05cm}\\
%
\textbf{51.} & * & \textit{Filling the gap with hierarchical black-hole mergers.}
\newline{}
4th World Laureates Forum, Shanghai, China, (online), Nov 2021.
\vspace{0.05cm}\\
%
\textbf{50.} & * & \textit{Inspiral, merge, repeat: hierarchical black-hole mergers and their gravitational-wave signatures.}
\newline{}
XXIV SIGRAV Conference 2021, Urbino, Italy, Sep 2021.
\vspace{0.05cm}\\
%
\textbf{49.} &  & \textit{Two precessing spins and how to find them.}
\newline{}
14th Edoardo Amaldi Conference, Melbourne, Australia, (online), Jul 2021.
\vspace{0.05cm}\\
%
\textbf{48.} &  & \textit{Waveform systematics and gravitational-wave catalogs.}
\newline{}
2nd European Physical Society Conference on Gravitation: measuring gravity, London, UK, (online), Jul 2021.
\vspace{0.05cm}\\
%
\textbf{47.} &  & \textit{Probing warped accretion disks with gravitational-wave observations of supermassive black-hole mergers.}
\newline{}
European Astronomical Society Annual Meeting (EAS2021), Leiden, The Netherlands, (online), Jun 2021.
\vspace{0.05cm}\\
%
\textbf{46.} & * & \textit{Hierarchical black-hole mergers in the LIGO/Virgo band.}
\newline{}
Gravitational Wave Astrophysics Conference 2021, Hefei, China, (online), Jun 2021.
\vspace{0.05cm}\\
%
\textbf{45.} &  & \textit{Testing GR? Keep calm and mind the waveform.}
\newline{}
24rd Capra Meeting on Radiation Reaction in General Relativity, Waterloo, Canada, (online), Jun 2021.
\vspace{0.05cm}\\
%
\textbf{44.} &  & \textit{Warped accretion disks with LISA.}
\newline{}
Distorted astrophysical discs: new insights and future directions, Cambridge, UK (online), May 2021.
\vspace{0.05cm}\\
%
\textbf{43.} &  & \textit{Detectability of gravitational-wave signals with neural-network classifiers.}
\newline{}
RAS Specialist Meeting -- Machine learning and artificial intelligence applied to astronomy 2, (online), May 2021.
\vspace{0.05cm}\\
%
\textbf{42.} & * & \textit{Transitioning to research independence in gravitational-wave astronomy (my own view on postdoc and grant applications).}
\newline{}
Gravitational Wave Astrophysics for Early Career Scientists, Leiden, The Netherlands, (online), May 2021.
\vspace{0.05cm}\\
%
\textbf{41.} &  & \textit{Can a computer learn if LIGO and Virgo will observe gravitational waves?.}
\newline{}
April APS Meeting, (online), Apr 2021.
\vspace{0.05cm}\\
%
\textbf{40.} &  & \textit{A self-consistent treatment of warped accretion disks surrounding spinning supermassive black holes.}
\newline{}
Science at the Horizon: the Next-Generation EHT, (online), Feb 2021.
\vspace{0.05cm}\\
%
\textbf{39.} & * & \textit{Astrophysical black-hole binaries: the elephant in the room.}
\newline{}
Primordial black holes confront gravitational-wave data, Rome, Italy, (online), Feb 2021.
\vspace{0.05cm}\\
%
\textbf{38.} & * & \textit{Black holes, gravitational waves, and the BEARs.}
\newline{}
10th Birmingham Environment for Academic Research (BEAR) Conference, Birmingham, UK, (online), Sep 2020.
\vspace{0.05cm}\\
%
\textbf{37.} &  & \textit{Warped accretion discs, black-hole spins, and LISA.}
\newline{}
13th LISA Symposium, (online), Sep 2020.
\vspace{0.05cm}\\
%
\textbf{36.} &  & \textit{Multi-timescale post-Newtonian dynamics of spinning black-hole binaries: a status update.}
\newline{}
23rd Capra Meeting on Radiation Reaction in General Relativity, Austin TX, USA, (online), Jun 2020.
\vspace{0.05cm}\\
%
\textbf{35.} & * & \textit{An attempt to navigate the astro job market.}
\newline{}
LISA Early Career Scientists (LECS) training workshop (online), Jun 2020.
\vspace{0.05cm}\\
%
\textbf{34.} &  & \textit{Second-generation black holes, the pair-instability mass gap, and the escape speed of stellar clusters.}
\newline{}
30th Texas Symposium on Relativistic Astrophysics, Portsmouth, UK, Dec 2019.
\vspace{0.05cm}\\
%
\textbf{33.} &  & \textit{Testing the no-hair theorem with multiband black-hole binaries.}
\newline{}
30th Texas Symposium on Relativistic Astrophysics, Portsmouth, UK, Dec 2019.
\vspace{0.05cm}\\
%
\textbf{32.} &  & \textit{Multiband gravitational-wave (astro)physics.}
\newline{}
Gravitational-wave Excellence through Alliance Training (GrEAT) PhD school, Birmingham, UK, Nov 2019.
\vspace{0.05cm}\\
%
\textbf{31.} &  & \textit{Pick the right one: Bayesian model selection on catalogs of gravitational-wave events.}
\newline{}
22nd International Conference on General Relativity and Gravitation (GR22) and 13th Edoardo Amaldi Conference, Valencia, Spain, Jul 2019.
\vspace{0.05cm}\\
%
\textbf{30.} &  & \textit{Space-ground multiband detections. How many?.}
\newline{}
22nd International Conference on General Relativity and Gravitation (GR22) and 13th Edoardo Amaldi Conference, Valencia, Spain, Jul 2019.
\vspace{0.05cm}\\
%
\textbf{29.} & * & \textit{Black-hole kicks: how and where.}
\newline{}
Taipei Gravitational Wave Group (TGWG) Conference, Taipei, Taiwan, Oct 2018.
\vspace{0.05cm}\\
%
\textbf{28.} & * & \textit{Forming binary black holes out of stars.}
\newline{}
Taipei Gravitational Wave Group (TGWG) Conference, Taipei, Taiwan, Oct 2018.
\vspace{0.05cm}\\
%
\textbf{27.} & * & \textit{Getting ready: exploit LISA to improve LIGO's tests of General Relativity.}
\newline{}
Einstein Fellows Symposium 2018, Cambridge MA, USA, Oct 2018.
\vspace{0.05cm}\\
%
\textbf{26.} &  & \textit{Runaways: recoiling black holes and their gravitational-wave signatures.}
\newline{}
COSPAR 2018 42nd assembly, Pasadena CA, USA, Jul 2018.
\vspace{0.05cm}\\
%
\textbf{25.} &  & \textit{An unprecedented opportunity: black-hole spectroscopy with LISA forewarnings and LIGO optimizations.}
\newline{}
12th LISA Symposium, Chicago IL, USA, Jul 2018.
\vspace{0.05cm}\\
%
\textbf{24.} & * & \textit{What do LIGO's black holes remember?.}
\newline{}
April APS Meeting, Columbus OH, USA, Apr 2018.
\vspace{0.05cm}\\
%
\textbf{23.} &  & \textit{Modeling black hole kicks with waveform approximants.}
\newline{}
34rd Pacific Coast Gravity Meeting, Pasadena CA, USA, Mar 2018.
\vspace{0.05cm}\\
%
\textbf{22.} &  & \textit{Black holes from other black holes?.}
\newline{}
Gravity@Malta2018, Valletta, Malta, Jan 2018.
\vspace{0.05cm}\\
%
\textbf{21.} & * & \textit{The gravitational-wave astronomy revolution.}
\newline{}
2nd Milan Christmas Workshop, Milan, Italy, Dec 2017.
\vspace{0.05cm}\\
%
\textbf{20.} &  & \textit{Reanalysis of LIGO black-hole coalescences with alternative prior assumptions.}
\newline{}
IAU Symposium 338, Baton Rouge LA, USA, Oct 2017.
\newline{}
\textcolor{color1}{$\bullet$} Proceedings published by Cambridge University Press (2018).
\vspace{0.05cm}\\
%
\textbf{19.} & * & \textit{Careful with the priors: a reanalysis of LIGO black-hole coalescences.}
\newline{}
Einstein Fellows Symposium 2017, Cambridge MA, USA, Oct 2017.
\vspace{0.05cm}\\
%
\textbf{18.} &  & \textit{Empty galaxies to constrain black-hole superkicks.}
\newline{}
3rd Swinburne-Caltech Galaxy Workshop, Pasadena CA, USA, Sept 2017.
\vspace{0.05cm}\\
%
\textbf{17.} & * & \textit{Surprises from the spins: astrophysics and relativity with detections of spinning black-hole mergers.}
\newline{}
12th Edoardo Amaldi Conference, Pasadena CA, USA, (plenary talk), Jul 2017.
\newline{}
\textcolor{color1}{$\bullet$} Proceedings published by IoP (2018).
\vspace{0.05cm}\\
%
\textbf{16.} &  & \textit{Core collapse and compact-object formation to test General Relativity.}
\newline{}
LIGO Core Collapse Supernova Workshop, Pasadena CA, USA, Mar 2017.
\vspace{0.05cm}\\
%
\textbf{15.} &  & \textit{The curious and simple limit of equal-mass precessing black-hole binaries.}
\newline{}
33rd Pacific Coast Gravity Meeting, Santa Barbara CA, USA, Mar 2017.
\vspace{0.05cm}\\
%
\textbf{14.} & * & \textit{Spins remember: spin signatures of astrophysical black hole formation mechanisms.}
\newline{}
Strong Gravity and Binary Dynamics with Gravitational Wave Observations, Oxford MS, USA, Feb 2017.
\vspace{0.05cm}\\
%
\textbf{13.} &  & \textit{The kick is in the waveform: detection of black-hole recoils.}
\newline{}
The Dawning Era of Gravitational-Wave Astrophysics, Aspen CO, USA, Feb 2017.
\vspace{0.05cm}\\
%
\textbf{12.} &  & \textit{Kicked waveforms: prospects for direct detection of black hole recoils.}
\newline{}
``April'' APS Meeting, Washington DC, USA, Jan 2017.
\vspace{0.05cm}\\
%
\textbf{11.} & * & \textit{Getting the most out of gravitational-wave observations: kicks and spin precession.}
\newline{}
Einstein Fellow Symposium 2016, Cambridge MA, USA, Oct 2016.
\vspace{0.05cm}\\
%
\textbf{10.} &  & \textit{Averaging the average: multi-timescale analysis of precessing black-hole binaries.}
\newline{}
21st International Conference on General Relativity and Gravitation (GR21), New York NY, USA, Jul 2016.
\vspace{0.05cm}\\
%
\textbf{9.} &  & \textit{Differential accretion means differential alignment.}
\newline{}
BritGrav 16, Nottingham, UK, Apr 2016.
\vspace{0.05cm}\\
%
\textbf{8.} &  & \textit{A new instability to black-hole spin precession.}
\newline{}
28th Texas Symposium on Relativistic Astrophysics, Geneva, Switzerland, Dec 2015.
\vspace{0.05cm}\\
%
\textbf{7.} &  & \textit{Binary black-hole spin precession: a tale of three timescales.}
\newline{}
One Hundred Years of Strong Gravity, Lisbon, Portugal, Jun 2015.
\vspace{0.05cm}\\
%
\textbf{6.} &  & \textit{Giant and empty: black-hole occupation fraction in brightest cluster galaxies.}
\newline{}
BritGrav 15, Birmingham, UK, Apr 2015.
\vspace{0.05cm}\\
%
\textbf{5.} & * & \textit{Not so fast: gas-driven spin alignment in merging black-hole binaries.}
\newline{}
Milan Christmas Workshop, Milan, Italy, Dec 2014.
\vspace{0.05cm}\\
%
\textbf{4.} &  & \textit{Missing black holes in brightest cluster galaxies as evidence for the occurrence of superkicks.}
\newline{}
99 years of Black Holes, Potsdam, Germany, May 2014.
\vspace{0.05cm}\\
%
\textbf{3.} &  & \textit{Rival families: waveforms from resonant black-hole binaries as probes of their astrophysical formation history.}
\newline{}
3rd Session of the Sant Cugat Forum on Astrophysics, Sant Cugat, Spain, Apr 2014.
\newline{}
\textcolor{color1}{$\bullet$} Proceedings published by Springer (2015).
\vspace{0.05cm}\\
%
\textbf{2.} &  & \textit{Gravitational-wave signals from stellar-mass black-hole binaries in resonant configurations.}
\newline{}
BritGrav 14, Cambridge, UK, Mar 2014.
\vspace{0.05cm}\\
%
\textbf{1.} &  & \textit{Spin alignment effects in stellar mass black hole binaries.}
\newline{}
22nd Midwest Relativity Meeting, Chicago IL, USA, Sep 2012.
\vspace{0.05cm}\\
%
\end{longtable} }
\textcolor{color1}{\textbf{Talks at department seminars:}}
\vspace{-0.5cm}

\cvitem{}{\small\hspace{-1cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
%
\textbf{39.} & * & \textit{Comparing gravitational-wave data and stellar-physics predictions with deep learning.}
\newline{}
Theoretical Physics colloquium, University of Cambridge, Cambridge, UK, Feb 2023.
\vspace{0.05cm}\\
%
\textbf{38.} & * & \textit{Gravitational-wave data exploitation with deep learning.}
\newline{}
Astrophysics seminars, Universit\`{a}  degli Studi di Milano, Milan, Italy, Jan 2023.
\vspace{0.05cm}\\
%
\textbf{37.} & * & \textit{Some of the LIGO events might have merged a few times already.}
\newline{}
Gr@v seminars, Universidade de Aveiro, Aveiro, Portugal (online), Nov 2021.
\vspace{0.05cm}\\
%
\textbf{36.} & * & \textit{Entering the data-driven regime of gravitational-wave astronomy.}
\newline{}
Physics Department colloquium, Universit\`{a}  degli Studi di Milano-Bicocca, Milan, Italy (online), Oct 2020.
\vspace{0.05cm}\\
%
\textbf{35.} & * & \textit{Waiting for the next black-hole surprise, from the upper mass gap to GW190412.}
\newline{}
Gravity seminars, University of Mississippi, Oxford MS, USA (online), Jun 2020.
\vspace{0.05cm}\\
%
\textbf{34.} & * & \textit{Keep the black holes merging: cluster escape speed and the curious case of GW190412.}
\newline{}
Astronomy seminars, Cardiff University, Cardiff, UK (online), May 2020.
\vspace{0.05cm}\\
%
\textbf{33.} & * & \textit{Growing up: the next generation of black holes moves out of the cluster.}
\newline{}
Black Hole Initiative Colloquium, Harvard University, Cambridge MA, USA (online), Mar 2020.
\vspace{0.05cm}\\
%
\textbf{32.} & * & \textit{Multiple generations of black-hole mergers to pinpoint their astrophysical origin.}
\newline{}
Gravity seminars, University of Southampton, Southampton, UK, Feb 2020.
\vspace{0.05cm}\\
%
\textbf{31.} & * & \textit{Assembling multiple generations of black-hole mergers in the LIGO/Virgo band.}
\newline{}
Theoretical Astrophysics seminars, University of Leicester, Leicester, UK, Feb 2020.
\vspace{0.05cm}\\
%
\textbf{30.} & * & \textit{Predicting LIGO's black holes with LISA.}
\newline{}
AstroParticle seminars, Institute for Fundamental Physics of the Universe, Trieste, Italy, Nov 2019.
\vspace{0.05cm}\\
%
\textbf{29.} & * & \textit{Multiband gravitational waves: event rates, detectability, and tests of gravity.}
\newline{}
Particle Cosmology seminars, University of Nottingham, Nottingham, UK, Nov 2019.
\vspace{0.05cm}\\
%
\textbf{28.} & * & \textit{Understanding birth and growth of binary black holes with gravitational waves.}
\newline{}
Physics Colloquium, California State University Los Angeles, Los Angeles CA, USA, Feb 2019.
\vspace{0.05cm}\\
%
\textbf{27.} & * & \textit{The (astro)physics of black-hole mergers and their gravitational-wave emission.}
\newline{}
Physics and Astronomy Colloquium, California State University Northridge, Los Angeles CA, USA, Jan 2019.
\vspace{0.05cm}\\
%
\textbf{26.} & * & \textit{Model selection for large catalogs of gravitational-wave events.}
\newline{}
Cosmology seminars, Johns Hopkins University, Baltimore MD, USA, Nov 2018.
\vspace{0.05cm}\\
%
\textbf{25.} & * & \textit{How to kick black holes out of their galaxies.}
\newline{}
Strong Gravity Seminars, Perimeter Institute for Theoretical Physics, Waterloo, Canada, Sep 2018.
\vspace{0.05cm}\\
%
\textbf{24.} & * & \textit{(Astro)physical consequences of black-hole recoils.}
\newline{}
CITA Seminars, Canadian Institute for Theoretical Astrophysics, Toronto, Canada, Sep 2018.
\vspace{0.05cm}\\
%
\textbf{23.} & * & \textit{Black-hole spins and the astrophysics of LIGO's sources.}
\newline{}
AEI seminars, Albert Einstein Institute, Hannover, Germany, Apr 2018.
\vspace{0.05cm}\\
%
\textbf{22.} & * & \textit{Dynamics of spinning black-hole binaries as a tool to uncover their formation pathway.}
\newline{}
AEI seminars, Albert Einstein Institute, Potsdam, Germany, Mar 2018.
\vspace{0.05cm}\\
%
\textbf{21.} & * & \textit{Runaways: phenomenology and detectability of black-hole recoils.}
\newline{}
Theoretical Astrophysics seminars, University of Florida, Gainsville FL, USA, Mar 2018.
\vspace{0.05cm}\\
%
\textbf{20.} & * & \textit{Testing relativity with past and future supernova explosions.}
\newline{}
Physics colloquia, Montana State University, Bozeman MT, USA, Feb 2018.
\vspace{0.05cm}\\
%
\textbf{19.} & * & \textit{More astrophysics out of the first gravitational wave detections.}
\newline{}
GSSI seminars, Gran Sasso Science Institute, L'Aquila, Italy, Jan 2018.
\vspace{0.05cm}\\
%
\textbf{18.} & * & \textit{Where do binary black holes come from? How do we find out?.}
\newline{}
Theory seminars, Sapienza Universit\`a di Roma, Rome, Italy, Jan 2018.
\vspace{0.05cm}\\
%
\textbf{17.} & * & \textit{Monopole radiation, hyper scalarization and inverse chirps: the promise of testing gravity with stellar collapse.}
\newline{}
Steward Observatory lunch seminars, University of Arizona, Tucson AZ, USA, Nov 2017.
\vspace{0.05cm}\\
%
\textbf{16.} & * & \textit{Black-hole binary spin precession: from relativity to astronomy.}
\newline{}
GRITTS seminars, Massachusetts Institute of Technology LIGO Lab, Cambridge MA, USA, Oct 2017.
\vspace{0.05cm}\\
%
\textbf{15.} & * & \textit{Constraining the astrophysics behind the first LIGO detections.}
\newline{}
Physics colloquia, University of Texas at Dallas, Richardson TX, USA, Sep 2017.
\vspace{0.05cm}\\
%
\textbf{14.} & * & \textit{Binary black hole astrophysics with the first gravitational-wave events.}
\newline{}
Theory group seminars, Universitat de Barcelona, Barcelona, Spain, May 2017.
\vspace{0.05cm}\\
%
\textbf{13.} & * & \textit{Astrophysics with the first gravitational-wave events: from supernova asymmetries to multiple black-hole generations.}
\newline{}
GR seminars, Department of Applied Mathematics and Theoretical Physics, Cambridge, UK, May 2017.
\vspace{0.05cm}\\
%
\textbf{12.} & * & \textit{Black-hole binaries on the road to merger.}
\newline{}
Oskar Klein Center colloquia, Stockholms Universitet, Stockholm, Sweden, Jan 2017.
\vspace{0.05cm}\\
%
\textbf{11.} & * & \textit{A tale of astronomy and relativity: formation and evolution of black-hole binaries.}
\newline{}
Department seminars, Universit\`{a}  degli Studi di Milano, Milan, Italy, Apr 2016.
\vspace{0.05cm}\\
%
\textbf{10.} & * & \textit{A new paradigm for black-hole spin precession.}
\newline{}
Astrophysics seminars, University of Birmingham, Birmingham, UK, Feb 2016.
\vspace{0.05cm}\\
%
\textbf{9.} & * & \textit{New insights on binary black-hole spin precession.}
\newline{}
Relativity division seminars, Albert Einstein Institute, Potsdam, Germany, Feb 2016.
\vspace{0.05cm}\\
%
\textbf{8.} & * & \textit{Spontaneous scalarization: a promising avenue for gravitational-wave astronomy.}
\newline{}
GReCO seminars, Institut d'Astrophysique de Paris, Paris, France, Jan 2016.
\vspace{0.05cm}\\
%
\textbf{7.} & * & \textit{Innovative multi-timescale approach to binary black holes.}
\newline{}
Theoretical Astrophysics seminars, Universit\`{a}  degli Studi di Milano, Milan, Italy, Dec 2015.
\vspace{0.05cm}\\
%
\textbf{6.} & * & \textit{Stellar collapse in scalar-tensor theories of gravity: prospects for gravitational-wave astronomy.}
\newline{}
Gravity and Particles seminar, University of Nottingham, Nottingham, UK, Dec 2015.
\vspace{0.05cm}\\
%
\textbf{5.} & * & \textit{Core collapse and relativistic stars in scalar-tensor theories of gravity.}
\newline{}
Gravity seminars, STAG Research Center, Southampton, UK, Oct 2015.
\vspace{0.05cm}\\
%
\textbf{4.} & * & \textit{Binary black-hole spin alignment: gas-driven and relativistic inspiral.}
\newline{}
Wednesday seminars, Institute of Astronomy, Cambridge, UK, Jun 2015.
\vspace{0.05cm}\\
%
\textbf{3.} & * & \textit{Spin-orbit resonances: unveiling black-hole binary dynamics on both stellar-mass and supermassive scale.}
\newline{}
Gravitational Physics seminars, Cardiff University, Cardiff, UK, May 2014.
\vspace{0.05cm}\\
%
\textbf{2.} & * & \textit{Spin-orbit resonances: unveiling black-hole binary dynamics on both stellar-mass and supermassive scale.}
\newline{}
GR seminars, Department Applied Mathematics and Theoretical Physics, Cambridge, UK,  May 2014.
\vspace{0.05cm}\\
%
\textbf{1.} & * & \textit{Spin alignment and resonant plane in stellar mass black hole binaries.}
\newline{}
Lunch talks, Leiden Observatory, Leiden, The Netherlands, Jan 2012.
\vspace{0.05cm}\\
%
\end{longtable} }
\textcolor{color1}{\textbf{Lectures at PhD schools:}}
\vspace{-0.5cm}

\cvitem{}{\small\hspace{-1cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
%
\textbf{1.} & * & \textit{Introduction to gravitational waves (theory background).}
\newline{}
VIPER summer school on PTA GW astrophysics, Nashville TN, USA (online), Jul 2022.
\vspace{0.05cm}\\
%
\end{longtable} }
\textcolor{color1}{\textbf{Posters at conferences:}}
\vspace{-0.5cm}

\cvitem{}{\small\hspace{-1cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
%
\textbf{7.} &  & \textit{PRECESSION: efficient black-hole binary evolution with python.}
\newline{}
Mathematics and Big Data Showcase, Cambridge, UK, Apr 2016.
\vspace{0.05cm}\\
%
\textbf{6.} & * & \textit{Numerical relativity group at University of Cambridge.}
\newline{}
Einstein's Legacy: celebrating 100 years of general relativity, London, UK, Nov 2015.
\vspace{0.05cm}\\
%
\textbf{5.} & * & \textit{Formation and evolution of compact objects in relativity and modified gravity.}
\newline{}
5th DiRAC Science Day, Cambridge, UK, Sep 2015.
\vspace{0.05cm}\\
%
\textbf{4.} &  & \textit{New analytic solutions to binary black-hole dynamics: from spin precession to inspiral.}
\newline{}
Eurostrings 2015, Cambridge, UK, Mar 2015.
\vspace{0.05cm}\\
%
\textbf{3.} & * & \textit{Analytic solutions to binary black-hole spin precession: recalling Kepler's two-body problem.}
\newline{}
Compact objects as astrophysical and gravitational probes, Leiden, The Netherlands, Jan 2015.
\newline{}
\textcolor{color1}{$\bullet$} \textbf{Best  presentation award}.
\vspace{0.05cm}\\
%
\textbf{2.} &  & \textit{Efficient precession-averaged evolution of spinning black-hole binaries.}
\newline{}
RAS Specialist Meeting -- Towards gravitational-wave astronomy: data analysis techniques and challenges, London, UK, Dec 2014.
\vspace{0.05cm}\\
%
\textbf{1.} &  & \textit{Morphologies and binary transfer: a new approach to the post-newtonian dynamics of precessing black-holes binaries.}
\newline{}
DPG Physics School ``General Relativity @99'', Bad Honnef, Germany, Sep 2014.
\vspace{0.05cm}\\
%
\end{longtable} }
\textcolor{color1}{\textbf{Outreach talks:}}
\vspace{-0.5cm}

\cvitem{}{\small\hspace{-1cm}\begin{longtable}{rp{0.3cm}p{15.8cm}}
%
\textbf{11.} & * & \textit{Onde gravitazionali, buchi neri e dove trovarli.}
\newline{}
Fondazione Sacro Cuore, Milan, Italy, Sep 2022.
\vspace{0.05cm}\\
%
\textbf{10.} & * & \textit{Quando la gravit\`a viaggia.}
\newline{}
Astronomiamo Association, Italy, (online), Mar 2022.
\vspace{0.05cm}\\
%
\textbf{9.} & * & \textit{Hearing the Universe with gravitational waves.}
\newline{}
Bromsgrove Astronomical Society, Bromsgrove, UK, (online), Jun 2021.
\vspace{0.05cm}\\
%
\textbf{8.} & * & \textit{Esplorare l'Universo con le onde gravitazionali.}
\newline{}
Settimana dell'Astronomia, Fondazione Lombardia per l'Ambiente, Italy, (online), Apr 2021.
\vspace{0.05cm}\\
%
\textbf{7.} & * & \textit{Can black-hole binaries really make it?.}
\newline{}
University of Birmingham Astronomical Student Society,  Birmingham, UK, (online), Mar 2021.
\vspace{0.05cm}\\
%
\textbf{6.} & * & \textit{The (gravitational) sound of the Universe.}
\newline{}
Institute of Physics (IoP) Lecture Series, UK, (online), Dec 2020.
\vspace{0.05cm}\\
%
\textbf{5.} & * & \textit{Looking at the Universe with gravity.}
\newline{}
Marling School visit, Birmingham, UK, Feb 2020.
\vspace{0.05cm}\\
%
\textbf{4.} & * & \textit{Somewhere in between astronomy and relativity.}
\newline{}
Astronomy in the City, Birmingham, UK, Jan 2020.
\vspace{0.05cm}\\
%
\textbf{3.} & * & \textit{Gravitational waves: somewhere between astronomy and relativity.}
\newline{}
Malvern Physics Olympics, Great Malvern, UK, Oct 2019.
\vspace{0.05cm}\\
%
\textbf{2.} & * & \textit{Ride the wave (with gravity).}
\newline{}
Physics Day Experience, Birmingham, UK, Jun 2019.
\vspace{0.05cm}\\
%
\textbf{1.} & * & \textit{Onde gravitazionali: ascoltare l'Universo (anzich\'e solo vederlo?).}
\newline{}
Liceo Candia and Liceo Frassati, Seregno, Italy, Jan 2018.
\vspace{0.05cm}\\
%
\end{longtable} }